N-dimensional Tic Tac Toe, and Adventure in Modules

### 2017-05-12 paper/paper.tex
Let's sprinkle some pretty words on this - initial paper commit

  \section{Program description}
  % A list and brief description of all of the signatures, modules, and functors
  % in your project. In the description of signatures and modules, you should
  % highlight especially important types and functions. The goal of this section
  % is to guide the reader through your source code, putting things into their
  % proper context. It isn’t necessary to describe every helper function, but this
  % section should provide a reasonably complete overview of the content of your
  % project.

>>>>

  Our project initially began as a pokemon simulator but early on we realized
  that we could make better use of the SML module system by approaching the
  problem of simulating player-based games in a more abstract way.
  By doing this we could use the basic notion of what a game simulation required
  and isolate a pattern to follow for any number of games that fit this
  adversarial model.
  A game would then be a specific implementation - in our case tic tac toe -
  that used this pattern.

  \section{Program description}
  % A list and brief description of all of the signatures, modules, and functors
  % in your project. In the description of signatures and modules, you should
  % highlight especially important types and functions. The goal of this section
  % is to guide the reader through your source code, putting things into their
  % proper context. It isn’t necessary to describe every helper function, but this
  % section should provide a reasonably complete overview of the content of your
  % project.
  Our project is separated between the code that describes the game simulation
  and the code that used this to make a specific tic tac toe implementation.
  The game simulation is located in the \texttt{game.sml} file. The code for 
  tic tac toe implementation is spread out between \texttt{tictactoe.sml} and
  \texttt{matrix.sml}.
